Crystals

### 2017-06-11 doc/ms.tex
Editing the appendix

\subsection*{Windows}
The entire repository, including C++ and Python source code, and a Windows
executable, is hosted on Bitbucket. The URL for the git repository is

{\tt https://bitbucket.org/eggplantbren/crystals}

If you do not use git, the repository can simply be downloaded from

@@

and unzipped into any location on your computer.

>>>>

The entire repository, including C++ and Python source code, and a Windows
executable, is hosted on Bitbucket. The URL for the git repository is
For most users, we suggest simply using the pre-compiled Windows executable
{\tt main.exe} from the repository.

The repository can simply be downloaded from

@@

and unzipped into any location on your computer. To execute the program,
run {\tt main.exe}. You will be prompted to enter the filename of the text
file containing the data.
